{\let\clearpage\relax \chapter*{Abstract}}
\addcontentsline{toc}{chapter}{Abstract} 

This report has been produced as a part of the educational goals of the course PRJ3
at Ingeniørhøjskolen Aarhus, the Aarhus Acedemy of Engineering. The report contains a
thourough description of the working process, as well as documentation of the product's
software and hardware.
The mandatory requirements of this semester-project have consisted of the following four
elements:
\begin{itemize}
	\item The system must contain an application with a graphical user interface
	\item The system must include a database
	\item The system must contain network communication
	\item The system must employ techniques from other courses of the semester
\end{itemize}
This has concluded in the product Traffic Control which is a system for monitoring the traffic lights in the municipality of Randers. \\
Users must be able to access the system on different platforms.
A web application, web API and an Android application has been developed, all of which communicate through the network to a database.

The design process is inspired by the courses software design and softwaretest which has given an opportunity to parallel testing and deliverance of high quality software modules.
During the development process the ASE-model is used which has resulted in an iterative process and meant that many parts of the development process have been reviewed continuously. This has resulted in a successful project.

Enclosed is a zip-file containing complete documentation, source code, etc.


